Time slice analyses

### 2017-09-15 analyses/02-time-slice-analyses.Rmd
Updates on the time bins stuff

## The latest version of Claddis (on development on my own branch)
install_github("TGuillerme/Claddis")
library(Claddis)

## The latest version of dispRity 
install_github("TGuillerme/dispRity", ref = "release")
library(dispRity) 
```

@@

How to go about that????
Need to collate data ourselves or can we use strap?

@@

>>>>

## The latest version of Claddis (on development on my own branch)
if(!require(Claddis)) install_github("TGuillerme/Claddis")
library(Claddis)

## The latest version of dispRity 
if(!require(dispRity)) install_github("TGuillerme/dispRity", ref = "master")
library(dispRity) 
```
<!-- TG: I've switched to master branch for the new functions -->

@@

How to go about that????
Need to collate data ourselves or can we use strap?
<!-- TG: got all that covered with the new get.bin.ages function! -->

```{r}
## Get the stratigraphic ages
time_ages <- get.bin.ages(tree, type = "Age")

## Get the stratigraphic ages
time_epoch <- get.bin.ages(tree, type = "Epoch")

## Get the median age duration (to create equal time bins)
age_duration <- median(abs(diff(time_ages)))

## Get the number of ages (to create equal time bins)
age_length <- length(time_ages)

## Get the median epoch duration (to create equal time bins)
epoch_duration <- median(abs(diff(time_epoch)))

## Get the number of epochs (to create equal time bins)
epoch_length <- length(time_epoch)
```

With this data, I suggest we can explore these different scenarios:

Name | Type | Scenario | Based on
------------|----------|----------
un_bin_age  | unequal bins | stratigraphic ages | Ages durations
un_bin_epo  | unequal bins | stratigraphic epochs | Epoch durations
eq_bin_age_med  | equal bins   | median age bins | Median age duration
eq_bin_epo_med  | equal bins   | median epoch bins | Median epoch duration
eq_bin_age_len  | equal bins   | number of age bins | same number of ages but equal duration
eq_bin_epo_len  | equal bins   | number epoch bins | same number of epoch but equal duration
slice_age_med  | time slicing | median age slices | median age duration (+ our 4 "models" of evolution)
slice_epo_med  | time slicing | median epoch slices| median epoch duration (+ our 4 "models" of evolution)
slice_age_len  | time slicing | number of age slices | same number of ages but slices (+ our 4 "models" of evolution)
slice_epo_len  | time slicing | number of epoch slices | same number of epoch but slices (+ our 4 "models" of evolution)

What do you think?

@@

<!-- TG: Suggestion for a "testing the effect of binning/slicing" pipeline -->
